Who Needs Privacy?

### 2018-12-09 manuscript/manuscript.tex
- major updates on everything:     - mostly finished the analyses     - rewritten the methods, results, and abstract

\documentclass[man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Who Needs Privacy?},
            pdfauthor={Tobias Dienlin~\& Miriam Metzger},
            pdfkeywords={keywords},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\shorttitle{Who Needs Privacy?}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} University of Hohenheim\\\textsuperscript{2} University of California, Santa Barbara}
\keywords{keywords\newline\indent Word count: X}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

@@

\abstract{
Objective: This study analyzes how personality relates to peoples'
desire for privacy. Specifically, we investigated whether the syllogism
``I don't mind surveillance because I have nothing to hide'' is correct:
Do people who lack integrity (given they have something to hide) indeed
desire more privacy?

Method: Study 1 featured an online questionnaire (\emph{N} = 268,
\emph{M}\textsubscript{age} = 20 years, 72\% female) and Study 2 a
laboratory experiment (\emph{N} = 87, \emph{M}\textsubscript{age} = 20
years, 51\% female), where participants wrote an essay about past
negative, positive, or neutral behaviors to analyze effects on desire
for privacy.

Results: Study 1 showed that respondents who are more shy, less anxious,
and more risk averse desired more privacy. Respondents who self-reported
lacking integrity reported desiring more privacy from government and
more anonymity. Study 2 replicated these results and showed a
statistical trend (\emph{p} = .052) that writing about negative past
behaviors increased desire for interpersonal privacy. Moreover, the
integrity IAT showed significant relations with desire for privacy from
government.

Conclusion: It is possible to predict peoples' desire for privacy based
on their lack of integrity. However, other neutral personality facets
also explain desire for privacy. Hence, putting everyone who desires
privacy under general suspicion would be incorrect.

}

@@

In his novel \emph{The Circle}, ({\textbf{???}}) describes a dystopian
society in which people are gradually forfeiting their privacy. People
decide to become \enquote{transparent}, which means that they start
carrying a small camera around the neck in order to broadcast their
daily lives to the Internet. Eventually, this causes a societal
upheaval: \enquote{The pressure on those who hadn't gone transparent
went from polite to oppressive. The question, from pundits and
constituents, was obvious and loud: If you aren't transparent, what are
you hiding?} ({\textbf{???}}). The main argument being offered to
justify the surveillance is: \enquote{If you have nothing to hide, you
have nothing to fear.} This syllogism is familiar, given that it
commonly appears in also nonfictional conversations ({\textbf{???}}).
Consider, for example, the following tweet: \enquote{I don't download
illegally. I don't have anything on my comp{[}uter{]} to hide. Hell, I'm
sure the \#NSA gave up on me years ago.} ({\textbf{???}}).

Why do people desire privacy? To date there is only little research on
why people desire privacy and how the desire for privacy can be
predicted by aspects of personality. For example, and to the best of our
knowledge, so far no study exists that has analyzed the nothing-to-hide
argument from a scientific and empirical perspective. Why do some people
not care whether government agencies such as the NSA are collecting
their data ({\textbf{???}}), and why do others protest vehemently in
order to protect their privacy?

Answering this question is important: Given that government agencies are
collecting large amounts of data hoping to reduce criminality and
terrorism, and given that government agencies are collecting this data
preemptively and without concrete suspicions, it is relevant to find out
whether this practice of mass surveillance can be justified based on the
nothing-to-hide argument. As a result, the main question of this paper
is: Do people who desire more privacy really have more to hide and, more
generally, what are personality facets that determine peoples' overall
desire for privacy?

\hypertarget{desire-for-privacy}{%
\subsection{Desire for Privacy}\label{desire-for-privacy}}

Privacy captures the extent of voluntary withdrawal from others (Westin,
1967). Several models suggest that privacy is a multi-dimensional
concept: For example, in a theory-driven treatise ({\textbf{???}})
argued that privacy has four dimensions: informational, social,
psychological, and physical privacy. Pedersen (1979), by contrast, did
an empirical factor analysis (initially starting with 94 items) and
suggested that privacy exists on six dimensions: reserve, isolation,
solitude, intimacy with friends, intimacy with family, and anonymity. In
addition, Schwartz (1968) differentiated between horizontal and vertical
privacy: Whereas horizontal privacy captures withdrawal from peers,
vertical privacy refers to withdrawal from superiors or institutions
(e.g., government agencies). Next to being multi-dimensional, privacy is
also contingent (Dienlin, 2014): One can, for example, distinguish
between the objective privacy context, the subsequent subjective
perception of privacy, the psychological desire for privacy (which is
both a situational and dispositional need), and the resulting privacy
behavior (as represented by self-disclosure). For the purpose of this
study, we combine the aforementioned theories and focus on (a) vertical
privacy with regard to the desire for withdrawal from government
surveillance, (b) horizontal privacy in terms of the desire for
withdrawal from peers, friends, or acquaintances, and (c) both
horizontal and vertical privacy as captured by the general desire for
anonymity.

\hypertarget{the-relation-between-integrity-and-desire-for-privacy}{%
\subsubsection{The relation between integrity and desire for
privacy}\label{the-relation-between-integrity-and-desire-for-privacy}}

Which specific aspects of personality help predict desire for privacy?
At its core, the nothing-to-hide argument implies that lack of integrity
is an important predictor of why people desire privacy. This becomes
especially apparent when we consider the definition of Solove's (2007)
nothing-to-hide argument (notably, Solove is a strong critic of the
nothing-to-hide argument):

The NSA surveillance, data mining, or other government information
gathering programs will result in the disclosure of particular pieces of
information to a few government officials, or perhaps only to government
computers. This very limited disclosure of the particular information
involved is not likely to be threatening to the privacy of law-abiding
citizens. Only those who are engaged in illegal activities have a reason
to hide this information. {[}({\textbf{???}}); p.~753{]}

This definition helps illustrate the link between lack of integrity and
desire for privacy: People who have \enquote{engaged in illegal
activities} can be considered, by definition, to lack integrity
({\textbf{???}}), which is why they have a reason \enquote{to hide this
information} (or, in other words, to desire more privacy). In terms of a
scientific definition of integrity there is no real consensus, however
most scholars agree that integrity \enquote{incorporates a tendency to
comply with social norms, avoid deviant behavior, and embrace a sense of
justice, truthfulness, and fairness} {[}({\textbf{???}}); p.~82{]}.

Several theoretical arguments exist why lack of integrity might
correlate with desire for privacy. In general, any self-disclosure is a
potential risk because others might disagree, disapprove, or misuse the
information in other contexts ({\textbf{???}}). Privacy regulation
theory showed that if self-disclosures are too risky, people raise their
desired level of privacy, intensify their boundary regulation, and
employ more mechanisms to seclude and protect themselves
({\textbf{???}}). In traditional contexts, this could range from
moderate behaviors like closing doors, to extreme behaviors such as
physically tossing someone out of the room ({\textbf{???}}). In modern
contexts, protecting one's privacy can mean to avoid photographs or to
deliberately shun public places that have surveillance cameras. People
who have actually committed something bad, treacherous, or illegal
become even more vulnerable and face a significant risk of
self-disclosure, because others will surely disapprove of these
activities ({\textbf{???}}). Hence, the foregoing arguments illuminate
an indirect link between integrity and desire for privacy: By
definition, people who participate in negative activities are considered
to lack integrity ({\textbf{???}}). People who have engaged in negative
activities have, by definition, more to hide, and disclosures concerning
those activities pose a high risk. Because of this increased risk,
people will arguably desire more privacy, as a means to mitigate their
felt risk ({\textbf{???}}). In this way, the current research extends
Altman's privacy regulation theory (1976) by suggesting that lack of
integrity is an important yet unexamined factor that could increase
peoples' desired level of privacy.

A few studies can be found that imply a relation between privacy and
integrity. For example, several studies found that surveillance reduces
cheating behaviors ({\textbf{???}}, Covey.1989). ({\textbf{???}}) asked
students to solve an impossible maze. In the high surveillance
condition, the experimenter stood in front of the students and closely
monitored their behavior. In the low surveillance condition, the
experimenter stood behind the students, did not monitor their behavior,
and visual dividers were used to block the experimenter's view of the
students. Results showed that students were more likely to cheat in the
low surveillance condition, suggesting that in situations of
surveillance (i.e., less privacy), people show fewer cheating behaviors
(i.e., more integrity). Similarly, people are more likely to prevent
others from stealing when security cameras are visible ({\textbf{???}}),
which is also a sign of higher integrity. Next, in a longitudinal sample
with 457 respondents in Germany ({\textbf{???}}), people who reported
needing more privacy were less satisfied with their lives (\emph{r} =
-.47), had more (\emph{r} = .41) and less positive affect (\emph{r} =
-.39). More importantly however, people who felt they needed more
privacy were also less authentic on their SNSs profiles (\emph{r} =
-.48) and less authentic in their personal relationships (\emph{r} =
-.28; {\textbf{???}}). For example, people who agreed to items like
\enquote{I do not talk about personal issues unless my conversation
partner brings them up first} were more likely to report that their
online profiles did not truly represent their personality. Given the
argument that authenticity is a subset of integrity ({\textbf{???}}), we
reason that the concept of integrity might relate to the desired level
of privacy. Finally, Pedersen (1982) showed that three dimensions of
need for privacy related to self-esteem: In his study with \emph{N} = 70
undergraduate students, respondents who held a lower self-esteem were
more reserved (\emph{r} = .29), needed more anonymity (\emph{r} = .21)
and preferred solitude (\emph{r} = .24). Granted, self-esteem and
integrity are generally distinct concepts; however, Pedersen's specific
operationalization of self-esteem integrated several aspects of
integrity (e.g., by using items such as \enquote{moral, nice, fair,
unselfish, good, honest, reputable, sane} to measure self-esteem). Thus,
our overarching hypothesis is that people who lack integrity have a
greater desire for privacy.

In Study 1, we used a questionnaire-based design to analyze how lack of
integrity and other personality facets relate to desire for privacy. In
accordance with the reasoning mentioned above, we suggest that people
with less integrity feel a greater desire for privacy. Specifically, we
argue that integrity may relate to the desire for privacy from (a)
government surveillance, as governments have the legitimate power to
prosecute illegal activities. Next, we hypothesize that integrity
relates to the desire privacy for (b) anonymity. Anonymity makes it more
difficult for both legal and social agents to identify and address
potential wrongdoers, which is why people with less integrity will
prefer situations in which they are anonymous. Finally, lack of
integrity likely also relates to an increased desire for privacy from
(c) other people, as most other people will disapprove of immoral or
illegal activities, and might reveal those activities to authorities.

Hypothesis 1: People who feel lower in self-perceived integrity desire
more privacy from government surveillance (H1a), more anonymity (H1b),
and more privacy from other persons (H1c).

\hypertarget{shyness}{%
\subsubsection{Shyness}\label{shyness}}

Critics of the nothing-to-hide argument hold that people who desire
privacy should not automatically be confronted with suspicion, and that
privacy has several purposes that are not related to criminal behavior
({\textbf{???}}). Westin (1967), for example, defined four primary
purposes of privacy: (1) self-development (i.e., the integration of
experiences into meaningful patterns), (2) autonomy (i.e., the desire to
avoid being manipulated and dominated), (3) emotional release (i.e., the
release of tension from social role demands), and (4) protected
communication (i.e., the ability to foster intimate relationships).
These are all important social factors for which people desire privacy.
Hence, the argument is that people who desire privacy can have several
legitimate reasons for doing so; reasons which are essential for
psychosocial wellbeing and which relate to different factors of
personality. Below, we thus explore other (neutral) aspects of
personality that potentially predict desire for privacy. In order to be
more precise, we follow the advice by Paunonen and Ashton (2001) and,
instead of using generic personality factors as predictors, refer to
specific personality facets.

First, we argue that people who are more reserved, who feel less
comfortable in social situations, generally desire more anonymity and
more interpersonal privacy. Given that privacy is, by definition, a
voluntary withdrawal from society (Westin, 1967), we expect that people
who are more reserved or more shy desire more privacy from others.
Several empirical studies support this hypothesis: Extroverted people
desire less privacy ({\textbf{???}}), people who describe themselves as
introverted thinkers are more likely to prefer social isolation
(Pedersen, 1982), and introverted people are more likely to report
invasions of privacy ({\textbf{???}}). Finally, we did not find
convincing theoretical and empirical arguments for why shyness should
relate to an increased desire for privacy from government surveillance,
which is why we did not include a hypothesis on this relation.

Hypothesis 2: People who are more shy desire more anonymity (H2a) and
more privacy from other persons (H2b).

@@

Of course, there are also reasons why people might desire less privacy.
Government agencies often curtail privacy with the aim to prevent crime:
For example, the NSA's surveillance programs are often considered a
direct response to the 9 / 11 terrorists attacks ({\textbf{???}}). It
seems plausible that people who are more afraid of terrorist attacks are
also more likely to consent to these surveillance programs, given that
these programs promise to reduce the likelihood of future attacks. One
can then argue that people who are afraid of terrorist attacks are also
more afraid of threats overall, which is why we suggest that people who
are, in general, more anxious desire less privacy from government
surveillance and less anonymity. We did not include a hypothesis on the
potential relation between anxiety and desire for interpersonal privacy.
On the one hand, one could argue that people who are more anxious are
more reserved, given that social interactions can pose significant risks
(especially with strangers or weak ties; {\textbf{???}}). At the same
time, one could suggest that especially those people who are more
anxious desire less privacy from others (and especially their strong
ties), in order to cope better with their daily challenges. At the end,
given that we measure interpersonal privacy on a general level (and do
not distinguish between desire for privacy from (a) weak ties and (b)
strong ties), it seems plausible that both effects could cancel each
other out.

@@

Disclosing personal information always poses a certain risk, given that
others can misuse self-disclosed personal information in different
contexts, which can lead to severe consequences ({\textbf{???}}). Not
everyone will feel intimidated by this hypothetical threat---except
those who have a general tendency to avoid taking unnecessary risks. The
most cautious strategy to minimize risks of personal self-disclosures
would be, arguably, to keep as much information as possible private.
Hence, we suggest that people who are, in general, more risk averse have
a good reason to desire more privacy in all three aforementioned
contexts.

Hypothesis 4: People who are more risk averse desire more privacy from
government surveillance (H4a), more anonymity (H4b), and more privacy
from other persons (H4c).

@@

The personal computer and the Internet have rendered the world
increasingly digitized: Social interactions, purchases, and medical
treatments nowadays all produce digital traces, which can be combined
into accurate latent user profiles. Given the features of digital
information (i.e., information is persistent, searchable, reproducible,
and scalable; {\textbf{???}}), this allows for unprecedented ways and
degrees of surveillance. Mark Zuckerberg famously observed that privacy
is no longer a \enquote{social norm,} rather that people share personal
information ({\textbf{???}}). Hence, in order to be part of contemporary
life (e.g., by using SNSs), it seems necessary to give up some privacy.
However, arguably not everyone is willing to pay that price, and
especially people who are more conservative might prefer to stick to
their usual routines and decide against giving up their privacy. This is
supported by empirical research: Older people, who are generally less
open and more traditional ({\textbf{???}}), are more concerned about
their privacy than younger people ({\textbf{???}}). Taken together, we
suggest that people who are more traditional also desire more privacy in
all three aforementioned contexts.

Hypothesis 5: People who are more traditional desire more privacy from
government surveillance (H5a), more anonymity (H5b), and more privacy
from other persons (H5c).

@@

>>>>

\documentclass[man,floatsintext]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdftitle={Who Needs Privacy?},
            pdfauthor={Tobias Dienlin~\& Miriam Metzger},
            pdfkeywords={Privacy, personality, anonymity, integrity, SEM},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\shorttitle{Who Needs Privacy?}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} University of Hohenheim\\\textsuperscript{2} University of California, Santa Barbara}
\keywords{Privacy, personality, anonymity, integrity, SEM}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\usepackage{lineno}

@@

\abstract{
In this study we analyzes how personality relates to
peoples' need for privacy. For example, we analyze if the so-called
\enquote{nothing-to-hide} argument is correct: Do people who lack
integrity really desire more privacy? Moreover, we also analyze the
relation between need for privacy and sociability, anxiety, risk
aversion, and traditionality. Using an online questionnaire with
\emph{N} = 261 mostly student respondents, we found that it is possible
to predict a considerable part of peoples' need for privacy on the basis
of their personalities. For example, we indeed found that repondents who
reported less integrity than others also desired more anonymity.
Moreover, more traditional and more anxious respondents desired more
privacy from the government, while more risk averse and less sociable
respondents desired more privacy from other people. 
}

@@

In his novel \emph{The Circle}, Eggers (2013) describes a dystopian
society in which people are gradually forfeiting their privacy. One
after another becomes \enquote{transparent}: Carrying a small camera
around the neck, people begin to broadcast their daily lives to the
Internet. In the novel, this eventually causes a societal upheaval:
\enquote{The pressure on those who hadn't gone transparent went from
polite to oppressive. The question, from pundits and constituents, was
obvious and loud: If you aren't transparent, what are you hiding?}
(Eggers, 2013, p. 129).

With this study, we want to answer the following question. Why do people
desire privacy? To date there is only little research on why people
desire privacy and how the need for privacy can be predicted by aspects
of personality. Why do some people not care whether government agencies
such as the NSA are collecting their data (Greenwald, n.d.), and why do
others protest vehemently in order to protect their privacy?

We think that finding an answer to this question is important: Given
that government agencies are collecting large amounts of data hoping to
reduce criminality and terrorism, and given that government agencies are
collecting this data preemptively and without concrete suspicions, it
seems relevant to find out whether this practice of mass surveillance
can be justified based on the nothing-to-hide argument. As a result, the
main question of this paper is: Do people who desire more privacy really
have more to hide and, more generally, what are personality facets that
determine peoples' overall need for privacy?

\hypertarget{the-need-for-privacy}{%
\subsection{The Need for Privacy}\label{the-need-for-privacy}}

Privacy captures the extent of voluntary withdrawal from others (Westin,
1967). Several models suggest that privacy is a multi-dimensional
concept: For example, in a theory-driven treatise Burgoon (1982) argued
that privacy has four dimensions: informational, social, psychological,
and physical privacy. Pedersen (1979), by contrast, did an empirical
factor analysis (initially starting with 94 items) and suggested that
privacy exists on six dimensions: reserve, isolation, solitude, intimacy
with friends, intimacy with family, and anonymity. In addition, Schwartz
(1968) differentiated between horizontal and vertical privacy: Whereas
horizontal privacy captures withdrawal from peers, vertical privacy
refers to withdrawal from superiors or institutions (e.g., government
agencies).

Next to being multi-dimensional, privacy is also contingent (Dienlin,
2014): One can, for example, distinguish between the objective privacy
context, the subsequent subjective perception of privacy, the
psychological need for privacy (which is both a situational and
dispositional need), and the resulting privacy behavior (as represented
by self-disclosure). For the purpose of this study, we combine the
aforementioned theories and focus on (a) vertical privacy with regard to
the need for withdrawal from government surveillance, (b) horizontal
privacy in terms of the need for withdrawal from peers, friends, or
acquaintances, and (c) both horizontal and vertical privacy as captured
by the general need for anonymity.

Which specific aspects of personality help predict need for privacy? The
so-called nothing-to-hide argument states that \enquote{If you have
nothing to hide, you have nothing to fear.} At its core, the
nothing-to-hide argument implies that an important predictor of why
people desire privacy is their \emph{lack of integrity}. This becomes
especially apparent when we consider the definition of Solove's (2007)
nothing-to-hide argument (notably, Solove is a strong critic of the
nothing-to-hide argument):

\begin{quote}
\enquote{The NSA surveillance, data mining, or other government
information gathering programs will result in the disclosure of
particular pieces of information to a few government officials, or
perhaps only to government computers. This very limited disclosure of
the particular information involved is not likely to be threatening to
the privacy of law-abiding citizens. Only those who are engaged in
illegal activities have a reason to hide this information.} (Solove,
2007, p. 753)
\end{quote}

This definition helps illustrate the link between lack of integrity and
need for privacy: People who have \enquote{engaged in illegal
activities} can be considered, by definition, to lack integrity
(Paunonen, 2002), which is why they have a reason \enquote{to hide this
information} (or, in other words, to desire more privacy). In terms of a
scientific definition of integrity there is no real consensus, however
most scholars agree that integrity \enquote{incorporates a tendency to
comply with social norms, avoid deviant behavior, and embrace a sense of
justice, truthfulness, and fairness} (Connelly, Lilienfeld, \& Schmeelk,
2006, p. 82).

Several theoretical arguments exist why lack of integrity might
correlate with need for privacy. In general, any self-disclosure is a
potential risk because others might disagree, disapprove, or misuse the
information in other contexts (Petronio, 2010). Privacy regulation
theory showed that if self-disclosures are too risky, people raise their
desired level of privacy, intensify their boundary regulation, and
employ more mechanisms to seclude and protect themselves (Altman, 1976).
In traditional contexts, this could range from moderate behaviors like
closing doors, to extreme behaviors such as physically tossing someone
out of the room (Altman, 1976). In modern contexts, protecting one's
privacy can mean to avoid photographs or to deliberately shun public
places that have surveillance cameras. People who have actually
committed something bad, treacherous, or illegal become even more
vulnerable and face a significant risk of self-disclosure, because
others will surely disapprove of these activities (Petronio, 2010).
Hence, the foregoing arguments illuminate an indirect link between
integrity and need for privacy: By definition, people who participate in
negative activities are considered to lack integrity (Paunonen, 2002).
People who have engaged in negative activities have, by definition, more
to hide, and disclosures concerning those activities pose a high risk.
Because of this increased risk, people will arguably desire more
privacy, as a means to mitigate their felt risk (Altman, 1976). In this
way, the current research extends Altman's privacy regulation theory
(1976) by suggesting that lack of integrity is an important yet
unexamined factor that could increase peoples' desired level of privacy.

A few studies can be found that imply a relation between privacy and
integrity. For example, several studies found that surveillance reduces
cheating behaviors (Corcoran \& Rotter, 1987, Covey.1989). Covey,
Saladin, and Killen (1989) asked students to solve an impossible maze.
In the high surveillance condition, the experimenter stood in front of
the students and closely monitored their behavior. In the low
surveillance condition, the experimenter stood behind the students, did
not monitor their behavior, and visual dividers were used to block the
experimenter's view of the students. Results showed that students were
more likely to cheat in the low surveillance condition, suggesting that
in situations of surveillance (i.e., less privacy), people show fewer
cheating behaviors (i.e., more integrity). Similarly, people are more
likely to prevent others from stealing when security cameras are visible
(van Bommel, van Prooijen, Elffers, \& van Lange, 2014), which is also a
sign of higher integrity. Next, in a longitudinal sample with 457
respondents in Germany (Trepte, Dienlin, \& Reinecke, 2013), people who
reported needing more privacy were less satisfied with their lives
(\emph{r} = -.47), had more (\emph{r} = .41) and less positive affect
(\emph{r} = -.39). More importantly however, people who felt they needed
more privacy were also less authentic on their SNSs profiles (\emph{r} =
-.48) and less authentic in their personal relationships (\emph{r} =
-.28; Trepte et al., 2013). For example, people who agreed to items like
\enquote{I do not talk about personal issues unless my conversation
partner brings them up first} were more likely to report that their
online profiles did not truly represent their personality. Given the
argument that authenticity is a subset of integrity (Sheldon, 2004), we
reason that the concept of integrity might relate to the desired level
of privacy. Finally, Pedersen (1982) showed that three dimensions of
need for privacy related to self-esteem: In his study with \emph{N} = 70
undergraduate students, respondents who held a lower self-esteem were
more reserved (\emph{r} = .29), needed more anonymity (\emph{r} = .21)
and preferred solitude (\emph{r} = .24). Granted, self-esteem and
integrity are generally distinct concepts; however, Pedersen's specific
operationalization of self-esteem integrated several aspects of
integrity (e.g., by using items such as \enquote{moral, nice, fair,
unselfish, good, honest, reputable, sane} to measure self-esteem). Thus,
our overarching hypothesis is that people who lack integrity have a
greater need for privacy.

In accordance with the reasoning mentioned above, we suggest that people
with less integrity feel a greater need for privacy. Specifically, we
argue that integrity may relate to the need for privacy from (a)
government surveillance, as governments have the legitimate power to
prosecute illegal activities. Next, we hypothesize that integrity
relates to the desire privacy for (b) anonymity. Anonymity makes it more
difficult for both legal and social agents to identify and address
potential wrongdoers, which is why people with less integrity will
prefer situations in which they are anonymous. Finally, lack of
integrity likely also relates to an increased need for privacy from (c)
other people, as most other people will disapprove of immoral or illegal
activities, and might reveal those activities to authorities.

Hypothesis 1: People who feel lower in self-perceived integrity desire
more privacy from government surveillance (H1a), more anonymity (H1b),
and more privacy from other people (H1c).

\hypertarget{sociability}{%
\subsubsection{Sociability}\label{sociability}}

Critics of the nothing-to-hide argument hold that people who desire
privacy should not automatically be confronted with suspicion, and that
privacy has several purposes that are not related to criminal behavior
(Marlinspike, n.d.). Westin (1967), for example, defined four primary
purposes of privacy: (1) self-development (i.e., the integration of
experiences into meaningful patterns), (2) autonomy (i.e., the desire to
avoid being manipulated and dominated), (3) emotional release (i.e., the
release of tension from social role demands), and (4) protected
communication (i.e., the ability to foster intimate relationships).
These are all important social factors for which people desire privacy.
Hence, the argument is that people who desire privacy can have several
legitimate reasons for doing so; reasons which are essential for
psychosocial wellbeing and which relate to different factors of
personality. Below, we thus explore other (neutral) aspects of
personality that potentially predict need for privacy. In order to be
more precise, we follow the advice by Paunonen and Ashton (2001) and,
instead of using generic personality factors as predictors, refer to
specific personality facets.

First, we argue that people who are more reserved, who feel less
comfortable in social situations, generally desire more anonymity and
more interpersonal privacy. Given that privacy is, by definition, a
voluntary withdrawal from society (Westin, 1967), we expect that people
who are more reserved or more shy desire more privacy from others.
Several empirical studies support this hypothesis: Extroverted people
desire less privacy (Morton, 2013), people who describe themselves as
introverted thinkers are more likely to prefer social isolation
(Pedersen, 1982), and introverted people are more likely to report
invasions of privacy (Stone, 1986). Finally, we did not find convincing
theoretical and empirical arguments for why sociability should relate to
an increased need for privacy from government surveillance, which is why
we did not include a hypothesis on this relation.

Hypothesis 2: People who are more sociable desire less anonymity (H2a)
and less privacy from other people (H2b).

@@

Of course, there are also reasons why people might desire less privacy.
Government agencies often curtail privacy with the aim to prevent crime:
For example, the NSA's surveillance programs are often considered a
direct response to the 9 / 11 terrorists attacks (Greenwald, n.d.). It
seems plausible that people who are more afraid of terrorist attacks are
also more likely to consent to these surveillance programs, given that
these programs promise to reduce the likelihood of future attacks. One
can then argue that people who are afraid of terrorist attacks are also
more afraid of threats overall, which is why we suggest that people who
are, in general, more anxious desire less privacy from government
surveillance and less anonymity. We did not include a hypothesis on the
potential relation between anxiety and need for interpersonal privacy.
On the one hand, one could argue that people who are more anxious are
more reserved, given that social interactions can pose significant risks
(especially with strangers or weak ties; Granovetter, 1973). At the same
time, one could suggest that especially those people who are more
anxious desire less privacy from others (and especially their strong
ties), in order to cope better with their daily challenges. At the end,
given that we measure interpersonal privacy on a general level (and do
not distinguish between need for privacy from (a) weak ties and (b)
strong ties), it seems plausible that both effects could cancel each
other out.

@@

Disclosing personal information always poses a certain risk, given that
others can misuse self-disclosed personal information in different
contexts, which can lead to severe consequences (Altman, 1976). Not
everyone will feel intimidated by this hypothetical threat---except
those who have a general tendency to avoid taking unnecessary risks. The
most cautious strategy to minimize risks of personal self-disclosures
would be, arguably, to keep as much information as possible private.
Hence, we suggest that people who are, in general, more risk averse have
a good reason to desire more privacy in all three aforementioned
contexts.

Hypothesis 4: People who are more risk averse desire more privacy from
government surveillance (H4a), more anonymity (H4b), and more privacy
from other people (H4c).

@@

The personal computer and the Internet have rendered the world
increasingly digitized: Social interactions, purchases, and medical
treatments nowadays all produce digital traces, which can be combined
into accurate latent user profiles. Given the features of digital
information (i.e., information is persistent, searchable, reproducible,
and scalable; boyd, 2008), this allows for unprecedented ways and
degrees of surveillance. Mark Zuckerberg famously observed that privacy
is no longer a \enquote{social norm,} rather that people share personal
information (Johnson, n.d.). Hence, in order to be part of contemporary
life (e.g., by using SNSs), it seems necessary to give up some privacy.
However, arguably not everyone is willing to pay that price, and
especially people who are more conservative might prefer to stick to
their usual routines and decide against giving up their privacy. This is
supported by empirical research: Older people, who are generally less
open and more traditional (Donnellan \& Lucas, 2008), are more concerned
about their privacy than younger people (Fife \& Orjuel, 2012). Taken
together, we suggest that people who are more traditional also desire
more privacy in all three aforementioned contexts.

Hypothesis 5: People who are more traditional desire more privacy from
government surveillance (H5a), more anonymity (H5b), and more privacy
from other people (H5c).

\hypertarget{sociodemographic-variables}{%
\subsubsection{Sociodemographic
variables}\label{sociodemographic-variables}}

(Dear Miriam, I would like to add a short paragraph on how
sociodemographics relate to privacy. Relevant studies I can think of are
Park (2015), Tifferet (2019), Weinberger, Zhitomirsky-Geffet, and
Bouhnik (2017), Trepte et al. (2013). I haven't yet managed to write it,
maybe you have time?)

@@

\hypertarget{open-science}{%
\subsection{Open science}\label{open-science}}

The following information can be found in the online supplementary
material (OSM): the data, the study material, the syntax, unabridged
results, additional analyses, and a reproducible version of the
manuscript. Next to the variables reported here, we also collected
additional ones, which can be found in the OSM. We invite everyone to
for example rerun our analyses or to investigate novel research
questions. It is also possible to suggest changes and/or corrections to
the manuscript. The OSM can be found here:
\url{https://github.com/tdienlin/need_for_privacy/}.
